










```{r include=FALSE }
render_markdown()
opts_chunk$set(fig.path='./figs/bla',concordance=TRUE,tidy=TRUE)
```






# HowTo Get data from the EUROSTAT
## Author: A. Blejec















```{r Author:,echo=FALSE }
###############################################
##                                           ##
## (c) Andrej Blejec (andrej.blejec```nib.si)  ##
##                                           ##
###############################################
```
```{r initialize,echo=FALSE,results='hide',message=FALSE }
options(width=70)
library(Hmisc)
#library(xlsReadWrite)
```

## Introduction

To make reproducible reports from the EUROSTAT data, I will explore
the possibility to download data from their repository. They provide data in different formats, with footnotes and labels included or not included. The most promising for automatic retreival is the so called \bold{TSV} format which is in fact tab separated file. This file is included in the \file{.zip} or \file{.gz} file.

## Finding the file name

We will explore it later.

## Get the data

Asumming that we have the desired file code, we can get it by composing the
URL:

```{r  }
fcode <- "tps00001"
lfn <- paste(fcode,".tsv",sep="")
upre <- "http://epp.eurostat.ec.europa.eu/NavTree_prod/everybody/BulkDownloadListing?file=data/"
upost <- ".tsv.gz"
furl <-paste( upre,fcode,upost,sep="")
furl
```

```{r  }
temp <- tempfile()
download.file(furl,temp)
data <- read.table(gzfile(temp), sep="\t", header=TRUE, row.names=1,
na.strings=": ")
unlink(temp)
```

Show the data structure

```{r  }
str(data)
```

First few lines

```{r  }
head(data)
```

## Clean the data

Some data contain labels and can be suffixed with a space. So we have to clean the data.

```{r  }
X <- data
X <- as.data.frame( 
apply(X, 2, function(x) as.numeric(sapply(x, 
FUN=function(u) gsub("[[:alpha:][:blank:]]","",u)))))
dimnames(X)[[1]] <- dimnames(data)[[1]]
```

Show the structure
```{r  }
str(X)
```

and first few lines

```{r  }
head(X)
```
















## SessionInfo
{
```{r sessionInfo,results='asis',echo=FALSE }
cat(win.version(),"\n")
(sessionInfo())
cat("Project path:\\verb'",dirname(getwd()),"'\\\\\n")
mainFile <- commandArgs(trailingOnly = TRUE)
#
mainFilePath <- file.path("../doc", mainFile[1])
cat("Main file :\\verb'", mainFilePath, "'\n")
#
mainFile <- strsplit(mainFile,'.',fixed=TRUE)[[1]][1]
projectName <- rev((strsplit(dirname(getwd()), "/"))[[1]])[1]
#
```

### View as vignette
Project files can be viewed by pasting this code to **`R`** console:\\
```{r projectFiles,echo=FALSE,results='asis' }
cat('> projectName <-"',projectName,'"; ',sep="")
cat(' mainFile <-"',mainFile,'"',sep="")
#
```

```{r vignette,eval=FALSE }
commandArgs()
library(tkWidgets)
openPDF(file.path(dirname(getwd()),"doc",
paste(mainFile,"PDF",sep=".")))
viewVignette("viewVignette", projectName, #
file.path("../doc",paste(mainFile,"Rnw",sep=".")))
#
```



`Git Revision: ` gitCommitterUnixDate \gitAbbrevHash{} (\gitCommitterDate)} \hfill \copyright A. Blejec\\
` ` gitReferences} \hfill \verb'`r mainFilePath`'\\

}

```{r eval=FALSE,echo=FALSE }
# getrootpath <- function() {
# fp <- (strsplit(getwd(), "/"))[[1]]
# file <- file.path(paste(fp[-length(fp)], collapse = "/"))
# return(file)
# }
# fileName <- function(name="bla",ext="PDF") paste(name,ext,sep=".")
```



